Topological Equivariant Artist Model for Visualization Library Architecture

### 2021-11-22 paper/main.tex
nt

\begin{equation}
  \begin{tikzcd}
    & {} \arrow[dd, "\vartistc", Rightarrow, shorten=1.25em] & \\
\mathcal{\gbasec}^{op} \arrow[rr, "\sheafc(\dtotalc)", bend left] \arrow[rr, "\sheafc_{\vartistc}(\gtotalc)"', bend right] &  & \textcolor{section}{\bm{Set}}\\
    & {} &                            
\end{tikzcd}
\end{equation}

>>>>

\begin{equation}
  \begin{tikzcd}
    & {} \arrow[dd, "\vartistc", Rightarrow, shorten=1.25em] & \\
\mathcal{\gbasec}^{op} \arrow[rr, "\sheafc_{\vindex_*}(\dtotalc)", bend left] \arrow[rr, "\sheafc_{\vartistc}(\gtotalc)"', bend right] &  & \bm{Set}\\
    & {} &                            
\end{tikzcd}
\end{equation}

of sheaf functors 
\begin{equation}
  \label{eq:artist:sheaf_map}
  \vartist: \sheafc_{vindex_*}(\dtotal) \rightarrow \sheafc_{\vartist}(\gtotal)
\end{equation}
from the graphic base space category $\mathcal{\gbase}^{op}$ to different objects in \bm{Set}. This means that the following diagram commutes
